%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  STARTING HERE, DO NOT TOUCH ANYTHING 
%%%%%%% --------------------------------------------------------------------------------------

%%%% Define Document type
\documentclass[11pt,a4]{article}

%%%% Include Packages
\usepackage{latexsym}
\newcommand{\bold}[1]{ {\bfseries #1}}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
 \usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{tabularx}
\hypersetup{colorlinks=true,urlcolor=black}
\usepackage[11pt]{moresize}
\usepackage{setspace}
% \usepackage{fontspec}
\usepackage[inline]{enumitem}
\usepackage{ragged2e}
\usepackage{anyfontsize}

%%%% Set Margins
\usepackage[margin=2cm]{geometry}

%%%% Set Page Style
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%%%% Set URL Style
\urlstyle{same}

%%%% Set Indentation
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%%%% Set Secondary Color, Page Number Color, Footer Text
\definecolor{UI_blue}{RGB}{32, 64, 151}
\definecolor{HF_color}{RGB}{179, 179, 179}


%%%% Set Heading Format
\titleformat{\section}{
\color{UI_blue} \scshape \raggedright \large 
}{}{0em}{}[\vspace{-0.7cm} \hrulefill \vspace{-0.2cm}]
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  END OF "DO NOT TOUCH" REGION
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------



\begin{document}
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  HEADER
%%%%%%% --------------------------------------------------------------------------------------
\begin{center}
    \begin{minipage}[b]{0.24\textwidth}
            \large (267)-401-2843 \\
            \large \href{mailto:L.tsai@mail.utoronto.ca}{L.tsai@mail.utoronto.ca} 
    \end{minipage}% 
    \begin{minipage}[b]{0.5\textwidth}
            \center{     
            \Huge{   Lawrence Tsai}} \\ %
            \vspace{0.1cm}
            {\color{UI_blue} \Large{}}
    \end{minipage}% 
    \begin{minipage}[b]{0.33\textwidth}
            \flushright \small
            {\href{www.linkedin.com/in/lawtsai/}{www.linkedin.com/in/lawtsai/} } \\
            \href{https://github.com/lt77777}{https://github.com/lt77777} \\
            \href{https://lawrencetsai.me}
            {https://lawrencetsai.me}
    \end{minipage}   
    
\vspace{-0.15cm} 
{\color{UI_blue} \hrulefill}
\end{center}

\justify
\setlength{\parindent}{0pt}
\setlength{\parskip}{12pt}
\vspace{0.2cm}


%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  First 2 Lines
%%%%%%% --------------------------------------------------------------------------------------


Dear Hiring Manager:

I am beyond excited about applying to work starting summer of 2023! 
I am currently a third-year pursuing a Specialist in
 Mathematics with Physics applications with minors 
 in Computer Science and Chemistry at the University
  of Toronto-Trinity College. In the summer of 2022,
   I had the opportunity to work as a Software Engineer
    at Promise Robotics for 4 months in utilizing robotics
     for automated construction. I utilized \textbf{Python, Django,
      Docker, Machine Learning, and applied Physics} as the
       top intern contributor. I had the opportunity to work
        with programming the robots directly as well as full 
        stack development and code reviews with the databases and security of
         our API. Besides that, I am a senior strategy 
         engineer for the Blue Sky Solar Racing Team at 
         the University of Toronto. I conduct solar cell
          research (optics and bifacial cells), fabricate,
           and create simulations \textbf{(Matlab, Python, Parallel 
           Computing \& CAD)} to optimize the performance and
            design of a solar car. I am also on the optics 
            team of the UofT Aerospace Team Space System
             Division where I do numerical analysis \textbf{(Python)} 
             and optical research (grisms and holographic 
             gratings) of our satellite payload. I am also leading a team of 2 to 
             design tests for our optical bench prototype
              which is going to be part of a hyperspectral 
              imaging CubeSat to measure anthropogenic gas 
              emissions across Ontario, Canada in 2024.
               Some projects of mine include a webcam 
               diagnostic tool in coordination with Dr.
                Etienne Benard-Seguin and Jeremy Moreau
                 (University of Calgary) to diagnose 
                 strabismus using OpenCV and mediapipe. 
                 Another project of mine that I developed
                  was a friend-making webapp called Amigos
                   using \textbf{Java, Spring Framework, Figma, Thymeleaf, Javascript, CSS, and HTML} and deployed on \textbf{Azure}.
                    I have some skills but more importantly,
                     have an aptitude for learning that I 
                     would like to demonstrate to you. I am
                      a well-rounded person that speaks 4
                      languages, plays 3 instruments, and 
                      played 2 varsity sports (wrestling and 
                      track). \par
     Overall, I would like to state that:


-I have the \bold{Skills:} I am a critical thinker and eager learner with mastery in
\bold{Python, Java, and MATLAB}. I am also currently working towards mastering
\bold{C and C++} and am working towards a Self Driving Car 4-Course Specialization
through the University of Toronto.\par

-I have the \bold{Passion:} I spend the bulk of my free time curiously learning 
on the internet and talking to friends in the field. All part of the fun!\par
-I have the \bold{Character:} I am a lighthearted guy. I find pleasure in the
 connections and conversations in life  :)




%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  SIGNATURE
%%%%%%% --------------------------------------------------------------------------------------

\vspace{0.5cm}
\raggedright
Sincerely \\ Lawrence (Larry) Tsai \\ (267)-401-2843 \\ \href{mailto:L.tsai@mail.utoronto.ca}{L.tsai@mail.utoronto.ca}

\end{document}